Simulation study scripts

### 2020-05-14 results/README.Rmd
update readmes

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
- `README.Rmd` containing R-code to transform the .json files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as .RDS files.

# Requirements
Extracing data from the simulation output requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. All these requirements are listed in the `requirements.txt` file. If you've already installed this file in the `simulation_study` step, please skip this. If not, you can run the following in your terminal to install all requirements: 
```{bash, eval = FALSE}
pip install -r ../simulation_study/requirements.txt
```

Additionally, to create the plots and statistics in the manuscript you will need to install a specific branch of the asreview visualization package. Run the following in your terminal: 
```{bash, eval = FALSE}
# clone visualization package from GitHub
git clone https://github.com/GerbrichFerdinands/asreview-thesis-visualization.git
```

@@

# function for extracting all separate runs 
read_trials <- function(m){
   files <- list.files(paste0("one_seed/statistics/", m), pattern = "results_", recursive = TRUE, full.names=TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,9]

>>>>

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and `.json` statistics files produced by the two jupyter notebooks above. The plots are used in the manuscript, the data are further processed by this readme into tables before they are manuscript-ready.
- `README.Rmd` containing R-code to transform the `.json` files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as `.RDS` files.

# Requirements
Extracing data from the simulation output requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. All these requirements are listed in the `requirements.txt` file. If you've already installed this file in the `simulation_study` step, please skip this. If not, you can run the following in your terminal to install all requirements:

```{bash, eval = FALSE}
pip install -r ../simulation_study/requirements.txt
```

Additionally, to create the plots and statistics in the manuscript you will need to install a specific branch of the asreview visualization package. Run the following in your terminal:

```{bash, eval = FALSE}
# clone visualization package from GitHub
git clone https://github.com/GerbrichFerdinands/asreview-thesis-visualization.git
```

@@

# function for extracting all separate runs 
read_trials <- function(m){
   files <- list.files(paste0("one_seed/statistics/", m), pattern = "results_", recursive = TRUE, full.names=TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,4]

### 2020-05-14 simulation_study/README.Rmd
update readmes

---
title: "log"
output:   
  md_document:
    variant: markdown_github
bibliography: ../manuscript/manuscript/asreview.bib
---

This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews.

@@

# Requirements 
This study requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. 
All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following to install all requirements: 
```{bash, eval = FALSE}
pip install -r requirements.txt
```

>>>>

---
title: "Simulation study scripts"
output: github_document
bibliography: ../manuscript/manuscript/asreview.bib
---

This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews. The output

@@

# Requirements 
This study requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. 
All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following in your bash terminal to install all requirements:

```{bash, eval = FALSE}
pip install -r requirements.txt
```

This automatically installs asreview version 0.9.3 and several dependencies. Moreover, a specific branch of the asreview simulation extension should be installed. Run the following in your bash terminal:
```{bash, eval = FALSE}
git clone https://github.com/GerbrichFerdinands/asreview-thesis-simulation.git
```

And then, within the newly created directory, the following:
```{bash, eval = FALSE}
# install visualization package 
pip install . 
```
